---
title: "shadows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shadows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Calculate footprint for a day
Load library

```{r setup}
library(landtools)
```

Here is an example of how to calculate the footprint of the sun over a layer 
of buildings during the day. Lets see how the houses look: 

```{r}
layer <- casas01
layer
```
How do they look?
```{r}
mapview(layer)
```

And now calculate the gpkg for the whole day, lets say for the 21 of Decembre of 2021,
from 5 am to 23 am, by 60 min intervals. (Hours out of the sunrise sunset interval will be automatically not calculated)

```{r}
library(landtools)
layer <- casas01
dayfootprint(day = "2021-12-21", layer, H="Altura", outdir = "../outputs/", 
             tz = "Europe/Paris", Xmin = 30)
```
You can plot those layers (all within the .gpkg file):
```{r}
res <- st_read('../outputs/20211221_footprint/20211221.gpkg')
mapview(res, alpha.regions=0.1)
```
Calculate for several days:
```{r}
days <- c('2021-01-15','2021-04-15', '2021-08-15', '2021-11-15')
fps <- lapply(days, function(x) dayfootprint(x, layer,H='Altura', outdir='../outputs/', Xmin = 30))
```
Lets now show the results between these footprints in 4 diferent days along the year:
```{r}
t1 <- paste('Shadows footprints between', min(fps[[1]]$Name), 'and', max(fps[[1]]$Name))
l1 <- fps[[1]]
plot(Altura)
ggplot(fps[[1]])
m1 = tm_shape(l1)+tm_fill(alpha = 0.2)+tm_shape(layer)
m1
m1+tm_raster(alpha=0.5)


m2 <- mapview(fps[[2]])

grid.arrange(m1, m2, ncol = 2) 
```

